Title Goes Here

### 2020-05-22 analysis/paper/paper.Rmd
l

<!-- change over time -->
When looking at gender ratios among the membership in Society for California Archaeology from 1967 to 2016, @tushingham2017peer report a trend of women increasingly maintaining their society membership and the gender gap being shortened over the years. @tushingham2017peer focuses on 3 articles from journals published in _Journal of California and Great Basin Anthropology/ Journal of California Anrchaeology_ (JCGBA/JCA) and _California Archaeology_ (CA) and a non-peer reviewed Society for California Archaeology _Poroceedings_. When looking at the percentage of female lead authors of a total of 2617 authors, the proportion of female lead authors have been increasing statistically significantly with p < 0.01 from the Cochran-Armitage chi-square test for trend (@tushingham2017peer). This similar trend of closing the gender gap can also be seen in women's pursue of higher degree in archaeology, out of a total of 217 surveryed, we see that in the 1950s females have 0% that are what the authors considered as decade of highest degree while in the 1980s it grew to 9.7% and eventually to 46.1% in 2010s (@vanderwarker2018ucsb). In the same study by @vanderwarker2018uscb, it is important to note that data collected from University of California, Santa Barbara Gender Equity Project shows that there are still imbalance as a result of different pay rates, for example, breaking down annual income by 20000 groupings, there is a trend that women outpoportions men in the lower bracket of less than 20000, 21000 to 40000 and 41000 to 60000 where as men outproportions women in the upper bracket of 61000 to 80000 and 81000 to 100000 and greater than 100000 (@vanderwarker2018uscb). 
<!-- add one more -->
Something about Twitter

>>>>

When looking at gender ratios among the membership in Society for California Archaeology from 1967 to 2016, @tushingham2017peer report a trend of women increasingly maintaining their society membership and the gender gap being shortened over the years. @tushingham2017peer focuses on 3 articles from journals published in _Journal of California and Great Basin Anthropology/ Journal of California Anrchaeology_ (JCGBA/JCA) and _California Archaeology_ (CA) and a non-peer reviewed Society for California Archaeology _Poroceedings_. When looking at the percentage of female lead authors of a total of 2617 authors, the proportion of female lead authors have been increasing statistically significantly with p < 0.01 from the Cochran-Armitage chi-square test for trend (@tushingham2017peer). This similar trend of closing the gender gap can also be seen in women's pursue of higher degree in archaeology, out of a total of 217 surveryed, we see that in the 1950s females have 0% that are what the authors considered as decade of highest degree while in the 1980s it grew to 9.7% and eventually to 46.1% in 2010s (@vanderwarker2018ucsb). In the same study by @vanderwarker2018uscb, it is important to note that data collected from University of California, Santa Barbara Gender Equity Project shows that there are still imbalance as a result of different pay rates, for example, breaking down annual income by 20000 groupings, there is a trend that women outpoportions men in the lower bracket of less than 20000, 21000 to 40000 and 41000 to 60000 where as men outproportions women in the upper bracket of 61000 to 80000 and 81000 to 100000 and greater than 100000 (@vanderwarker2018uscb).

Something about Twitter
